---
title: 'Reproducible Research: Peer Assessment 1'
output: html_document
---

### Loading and preprocessing the data


- Read the dataset by completed sets, and get the sum of steps per day  
```{r}
rf <- read.csv("activity.csv", header = TRUE)
rf2 <- na.omit(rf)
steps_per_day <- aggregate(steps~date, rf2, sum)
```

### What is mean total number of steps taken per day


- Create the histogram of total number of steps in a day  
```{r}
hist(steps_per_day$steps, col=1, main="Total number of steps per day")
```


- Get the sum and medien of the steps as per date  
```{r}
mean(steps_per_day$steps)
median(steps_per_day$steps)
```

### What is the average daily activity pattern?


- Create line plot of steps of steps in interval   
```{r}
mean_per_interval <- aggregate(steps~interval, rf2, mean)
plot(mean_per_interval$interval, mean_per_interval$steps, type="l", col=1,
     main = "Average number of steps averaged over all days")
```


- Find the row of maximum average number of steps  
```{r}
mean_per_interval[which.max(mean_per_interval$steps),]
```

### Imputing missing values


- Get rows of NA's  
```{r}
rf_NA <- rf[!complete.cases(rf),]
nrow(rf_NA)
```


- Replacing NA by the mean of 5-minute interval, aggregate steps as per date
```{r}
for (i in 1:nrow(rf)){
  if(is.na(rf$steps[i])){
    interval_value <- rf$interval[i]
    row_id <- which(mean_per_interval$interval == interval_value)
    steps_value <- mean_per_interval$steps[row_id]
    rf$steps[i] <- steps_value
  }
}
steps_per_day_imputed <- aggregate(steps ~ date, rf, sum)
```


- Create histogram
```{r}
hist(steps_per_day_imputed$steps, col=1, main="Imputed histogram of total number of steps per day")
```


- Get the mean of total number of steps per day
```{r}
mean(steps_per_day_imputed$steps)
median(steps_per_day_imputed$steps)
```


* imputation of the data had changed the median slightly, but the mean remains the same


### Are there differences in activity patterns between weekdays and weekends?


- Seperate the data by weekdays and weekends  
- Somehow my R is using Korean so I have use sunday and saturday in Korean

```{r}
rf$date <- as.Date(rf$date)
rf$day <- weekdays(rf$date)
rf$day_type <- c("weekday")
for(i in 1:nrow(rf)){
  if (rf$day[i]=="토요일" || rf$day[i]=="일요일"){
    rf$day_type[i] <- "weekend"
  }
}
rf$day_type<- as.factor(rf$day_type)
mean_per_interval_imputed <- aggregate(steps ~ interval+day_type, rf, mean)
```

- Get the ggplot and create plot
```{r}
library(ggplot2)
qplot(interval, steps, data=mean_per_interval_imputed, facets = .~ day_type, geom=c("line"), xlab="Interval", 
      ylab="Number of steps", main="")
```

* And we can see there is difference between them.




